ASHA 2023 Listening Effort Data Analysis

### 2023-11-03 ASHA 2023 Analysis/data_analysis.Rmd
put code chunk on hold
normalizing the ALs trials is currently a wip. This commit is just saving the progress made so far. However, the code will not be evaluated when creating the rendered rmd document

```{r, include = F, eval = F}

bin.length = 26

@@

normed_pupil <- rbind(data1, control)

@@

normed_pupil %>%
  # Selecting relevant parameters
  dplyr::select(subject, trial, speaker, bins, code) %>%
  # Filtering out time before start of phrase
  dplyr::filter(bins >= 0) %>%
  dplyr::group_by(speaker, code) %>%
  dplyr::summarize(length = max(bins)) %>%
  dplyr::group_by(speaker) %>%
  dplyr::summarize(av_length = mean(length),
                   av_offset = av_length - 3000,
                   av_end_roi = av_length - 2000) %>%
  gt::gt() %>%
  gt::cols_label(speaker = "Speaker",
                 av_length = "Average Trial Length (ms)",
                 av_offset = "Average Phrase Length (ms)",
                 av_end_roi = "Average Endpoint for ROI (ms)")

>>>>

```{r, echo = F, eval = F}

# This code block is a Work in Progress. Since the phrase legnths between the ALS speaker and the Control speaker are very different, this block is attempting to downsample the ALS trials to be a similar length of the control trials. The current code is able to downsample to a point where the number of rows for ALS trials and control trials are similar (in the new normed_pupil df). However, the timestamp labels were not updated yet. This analysis may be moved to an alternative script to further flesh this out.

bin.length = 26.27

@@

@@

data %>%
  count(speaker, code) %>%
  group_by(speaker) %>%
  summarize(row_m = mean(n), sd = sd(n))
